---
title: "Us and them: Identity and polarization in contemporary democracies"
subtitle: "What it means for a democracy to be polarized, and what group identity has to do with it."
---

```{r}
#| label: setup-index
#| echo: false
#| message: false
#| warning: false

library(here) # project-root-relative paths
library(yaml) # read course.yml

# website/_quarto.yml is itself a project-root marker, so a bare here() would stop at
# website/ rather than the repo root. i_am() anchors it explicitly. See STYLE.md section 4.
here::i_am("website/index.qmd")
source(here("website", "_course-helpers.R"))

# shown() prints an honest "to be announced" for any key still PLACEHOLDER in
# course.yml, which is where every value on this page comes from.
cfg <- read_course()
```

`r shown(cfg$course$term)`<br>
`r cfg$course$department`<br>
`r cfg$course$school`<br>
`r cfg$course$university`

::: {.home}

:::: {.grid .course-details}

::: {.g-col-12 .g-col-md-4}

### Instructor {#sec-instructor}

- {{< fa user >}} `r cfg$course$instructor`
- {{< fa university >}} `r cfg$course$office`
- {{< fa envelope >}} [`r cfg$course$email`](mailto:`r cfg$course$email`)

:::

::: {.g-col-12 .g-col-md-4}

### Course details {#sec-course-details}

- {{< fa calendar >}} `r shown(cfg$sessions$weekday)`
- {{< fa clock >}} `r shown(cfg$sessions$time)`
- {{< fa location-dot >}} `r shown(cfg$sessions$room)`
- {{< fa list-ol >}} `r cfg$sessions$count` sessions, one per week
- {{< fa pen-nib >}} Term paper, max. `r cfg$paper$max_words` words
- {{< fa award >}} `r cfg$course$ects` ECTS

:::

::: {.g-col-12 .g-col-md-4}

### Contacting me {#sec-contact}

- {{< fa calendar-check >}} **Office hours:** `r shown(cfg$sessions$office_hours)`

:::

::::

:::

## What this course is {#sec-what-this-is}

```{r}
#| label: what-this-is
#| echo: false
#| results: asis

# Written once in course.yml, printed here and on the syllabus, so the two cannot drift.
cat(trimws(cfg$course$description), "\n\n")
```

The last three sessions belong to your term paper: two of short pitches to the group, and one of optional individual consultation.

## Where to go next {#sec-where-next}

- **[Syllabus](syllabus.qmd)** for the full details: objectives, logistics, what is required of
  you, the policies, and what each session covers and asks you to read.
- **[Schedule](schedule.qmd)** for the dates, the topics and the slides.
