---
title: "Schedule"
toc: true
toc-depth: 2
---

```{r}
#| label: setup-schedule
#| echo: false
#| message: false
#| warning: false

library(here) # project-root-relative paths
library(yaml) # read course.yml

# website/_quarto.yml is itself a project-root marker, so a bare here() would stop at
# website/ rather than the repo root. i_am() anchors it explicitly. See STYLE.md section 4.
here::i_am("website/schedule.qmd")
source(here("website", "_course-helpers.R"))

cfg <- read_course()
```

Your roadmap for the term.
One session per week, and each row links the session's slides and its entry in the
[Syllabus](syllabus.qmd), which is where the readings and the learning goals live.

::: {.schedule-legend}
| | |
|---|---|
| {{< fa chalkboard >}} | **Slides.** The session's deck. |
| {{< fa book >}} | **Reading.** Opens the session's entry in the syllabus, core and optional. |
| [{{< fa chalkboard >}}]{.schedule-tbd} | Greyed out means not published yet. |
| [none]{.schedule-none} | There is no reading for that session at all. |
:::

::: {.callout-note}
This is a preliminary plan and may be revised during the term.
Greyed-out entries are not settled yet.
:::

```{r}
#| label: schedule-tables
#| echo: false
#| message: false
#| warning: false
#| results: asis

# -----------------------------------------------------------------------------
# These tables are BUILT, not typed. Sources of truth:
#   course.yml                -> session count, block names, per-session topics
#   website/slides/weekNN.qmd -> the session's deck, linked once the file exists
# Dates come from session_dates(), which starts at first_session and skips the
# cancelled dates, so a cancelled session pushes the later ones back rather than
# renumbering the term. A slide link appears as soon as its deck exists, so there
# is nothing to remember to switch on at release.
# cfg / pad() / the block helpers come from the setup chunk and _course-helpers.R.
# -----------------------------------------------------------------------------
n_wk <- cfg$sessions$count
dates <- session_dates(cfg)

# Grey, not a link: planned but not settled.
planned <- function(x) sprintf("[%s]{.schedule-tbd}", x)
tbd <- planned("--")

# The two link columns are icons rather than words, so a row stays narrow. The
# fontawesome shortcode is emitted as text here and resolved by Quarto after
# knitr has run, which is why an asis chunk can write one.
icon <- function(name) sprintf("{{< fa %s >}}", name)
icon_link <- function(name, href) sprintf("[%s](%s)", icon(name), href)
icon_off <- function(name) sprintf("[%s]{.schedule-tbd}", icon(name))

topic_of <- function(i) {
  w <- week_entry(cfg, i)
  if (is.null(w) || is.null(w$topic)) tbd else w$topic
}

# The deck for a session, by convention website/slides/weekNN.qmd. The link is
# gated on the file existing, so a deck publishes itself and course.yml carries no
# slides key that could fall out of step with what is actually written.
deck_of <- function(i) here("website", "slides", paste0("week", pad(i), ".qmd"))

slides_of <- function(i) {
  if (file.exists(deck_of(i))) {
    icon_link("chalkboard", sprintf("slides/week%s.html", pad(i)))
  } else {
    icon_off("chalkboard")
  }
}

# The readings live in the syllabus, so the schedule links there rather than
# repeating them. The anchor is the one syllabus.qmd emits for the session.
# A session with no readings at all says so, because that is a different claim
# from a greyed icon, which means not published yet.
reading_of <- function(i) {
  n <- length(readings_of(cfg, i, "core")) + length(readings_of(cfg, i, "optional"))
  if (n == 0) {
    return("[none]{.schedule-none}")
  }
  icon_link("book", sprintf("syllabus.html#sec-session-%s", pad(i)))
}

row_of <- function(i) {
  sprintf(
    "| %s | %s | %s | %s | %s |",
    pad(i), session_date_label(dates, i), topic_of(i), slides_of(i), reading_of(i)
  )
}

# A cancelled date, printed where it falls so the gap in the dates is explained.
skip_row <- function(d) {
  sprintf("| %s | %s | %s | | |", tbd, format(d, "%d %b"), planned("No session"))
}

header <- c(
  "| Session | Date | Topic | Slides | Reading |",
  "|--------:|:-----|:------|:------:|:-------:|"
)

skips <- skipped_sessions(cfg)

emit_table <- function(weeks, caption, id) {
  rows <- vapply(weeks, row_of, character(1))
  # Any cancelled date that falls inside this block's span goes in at its place.
  for (k in seq_len(nrow(skips))) {
    aw <- skips$after_week[k]
    if (aw %in% weeks) {
      at <- which(weeks == aw)
      rows <- append(rows, skip_row(skips$date[k]), after = at)
    }
  }
  cat(c(header, rows), sep = "\n")
  cat("\n\n: ", caption, " {#", id, "}\n\n", sep = "")
}

emit_table(
  1,
  "Session 1, orientation. What the seminar asks, how the term is organised, and what a term paper in it looks like.",
  "tbl-schedule-session1"
)

for (k in seq_along(cfg$blocks)) {
  b <- cfg$blocks[[k]]
  weeks <- seq(b$from, min(b$to, n_wk))
  cat("#### Block ", block_numeral(k), ": ", b$name, "\n\n", sep = "")
  emit_table(
    weeks,
    sprintf(
      "Block %s of the term, %s. The chalkboard opens the session's slides and the book opens its entry in the syllabus, where the core and optional readings are listed. A greyed icon is not published yet.",
      block_numeral(k), tolower(b$name)
    ),
    sprintf("tbl-schedule-block%d", k)
  )
}
```

## How a session runs {#sec-how-a-session-runs}

Everyone reads the **core reading** beforehand, and the session is a discussion of that text
rather than a lecture about it.
I open with a short framing of the reading and the questions it raises, and the rest of the time
belongs to the group.
The optional readings are there for anyone who wants to go further, and as a starting point for
term papers.

Sessions `r cfg$blocks[[4]]$from` and `r cfg$blocks[[4]]$from + 1` are term paper pitches, and
session `r cfg$sessions$count` is optional individual consultation.
See [what is required of you](syllabus.qmd#sec-requirements) for what each of those asks.
