---
title: "Syllabus"
toc: true
toc-depth: 3
---

```{r}
#| label: setup-syllabus
#| echo: false
#| message: false
#| warning: false

library(here) # project-root-relative paths
library(yaml) # read course.yml

# website/_quarto.yml is itself a project-root marker, so a bare here() would stop at
# website/ rather than the repo root. i_am() anchors it explicitly. See STYLE.md section 4.
here::i_am("website/syllabus.qmd")
source(here("website", "_course-helpers.R"))

cfg <- read_course()

# Session numbers referenced in the prose come from course.yml, never typed.
n_sessions <- cfg$sessions$count
```

## Course description {#sec-course-description}

```{r}
#| label: course-description
#| echo: false
#| results: asis

# Written once in course.yml, printed here and on the About page, so the two cannot drift.
cat(trimws(cfg$course$description), "\n\n")
```

## Course objectives {#sec-course-objectives}

The seminar is built around reading political science carefully rather than accumulating results.
By the end of it you should be able to take a claim about polarization, work out what it is a claim about, and say what evidence would support or undermine it.

Three things run through every session.
The first is **conceptual discipline**: polarization means several different things, and many disagreements in this literature are about which one is meant.
The second is **measurement**: an affective polarization score is a construction, and what it is built from shapes what it can support.
The third is **evidence**: a striking finding is a starting point rather than a conclusion, and the seminar asks what design produced it and how much it can carry.

The term paper is where you do this on a question of your own.

## Course logistics {#sec-logistics}

### General information {#sec-general-information}

The seminar meets on `r shown(cfg$sessions$weekday)`s, `r shown(cfg$sessions$time)`, in
`r shown(cfg$sessions$room)`.
Each session is built around the core reading, so the discussion only works if everyone has done
it.
Readings for each session are listed in @sec-session-plan and the full references are collected
in @sec-references.

::: {.callout-tip}
**If you have to miss a session, tell me beforehand.**
A short email is enough, and it lets me tell you what you missed.
:::

### Prerequisites {#sec-prerequisites}

Two different things go by this name, and it is worth keeping them apart.

**Formally**, the prerequisite depends on which of the two modules in @sec-module you register
this seminar under.
Whether you meet it is a question for the module catalogue and the Studienbüro, not for me.

**In terms of what this course assumes**, no prior work on polarization, party systems or
political psychology is expected.
The readings are research articles rather than textbook chapters, so you should be comfortable
reading one, but learning how to read one is part of what the seminar is for.

### Module and credits {#sec-module}

This seminar is offered in **both** International Relations modules, and which one applies to you
depends on how you register it.
The credits, the assessment and the term paper word limit are the same either way.
It counts toward either of:

```{r}
#| label: module-list
#| echo: false
#| results: asis

# Built from cfg$course$modules so the module names cannot drift from course.yml.
for (m in cfg$course$modules) {
  cat(sprintf("- %s (Modulkatalog p. %s)\n", m$name, m$page))
}
cat("\n")
```

- **Course type:** `r cfg$course$course_type`
- **Credits:** `r cfg$course$ects` ECTS

The authoritative version of all of this is the
[module catalogue](https://www.sowi.uni-mannheim.de/studium/im-studium/pruefungen-und-ordnungen/)
and the
[examination regulations](https://www.sowi.uni-mannheim.de/studium/im-studium/pruefungen-und-ordnungen/)
for the B.A. Political Science, not this page.
Where the two disagree, the regulations win.

### What is required of you {#sec-requirements}

Assessment has two parts, and the vocabulary is the examination regulations' own.
**Coursework** (*Studienleistung*) is assessed pass or fail, and passing it is a prerequisite for
the graded work.
The **term paper** (*Prüfungsleistung*) carries the mark.

#### Coursework, pass or fail {#sec-coursework}

**1. Active participation (*Mitarbeit*).**
Section 13b of the examination regulations allows participation to be set as coursework in a
discussion-based course of this size, and it is set here.
It is assessed on the whole of your contributions across the term, not on any single session.
What counts is that you engage with the reading and with what other people say about it.

**2. Doing the reading.**
Each session lists **core reading**, which everyone does, and **optional reading**, which is there
for anyone who wants to go further and as a starting point for term papers.
The core reading is mandatory rather than recommended.
It is also the basis on which participation is assessed, because a discussion of a text nobody has
read is not a discussion.

**3. A term paper idea presentation (*Referat*).**
You pitch your term paper to the group in session `r cfg$blocks[[4]]$from` or
`r cfg$blocks[[4]]$from + 1`.
A few minutes on your question, why it is worth answering, and how you would answer it, followed
by discussion.
The point is to get criticism while there is still time to act on it.

#### Term paper, graded {#sec-term-paper}

- **Form:** a written term paper (*schriftliche Hausarbeit*).
- **Length:** at most **`r cfg$paper$max_words` words**, the limit set in the module catalogue.
- **Deadline:** `r shown(cfg$paper$deadline)`.
- **Topic:** your own, on something the seminar covers. You pitch it in session
  `r cfg$blocks[[4]]$from` or `r cfg$blocks[[4]]$from + 1`, and session `r n_sessions` is optional
  individual consultation.

A workable paper takes a claim from the literature and does something specific to it: tests it
against a case or a dataset it was not built on, takes apart a concept two authors are using
differently, or works out what a measurement choice does to a published conclusion.
A summary of what several authors have said is not a term paper.

### Registration and withdrawal {#sec-registration}

Registration for the *Prüfungsleistung*, deregistration, and the applicable deadlines are handled
by the **Studienbüro** under the examination regulations, not by me.
Check the dates there and keep to them, because responsibility for meeting them sits with you.

If a good reason, illness in particular, prevents you from submitting the term paper on time,
section 30 of the examination regulations applies.
You must submit a **written application to the Studienbüro without delay**, with evidence.
The examination board decides, and the burden of proof is on the applicant.
Tell me as well, but telling me is not a substitute for the formal application.

Section 5 additionally allows deadlines for coursework and examinations to be extended on a timely
written application, for instance for students with children or with dependants requiring care.

### Disability and chronic illness {#sec-accommodations}

If a disability or a chronic illness makes it harder for you to take an assessment in the form it
is set, you are entitled to compensation that restores equal opportunity, under section 6 of the
examination regulations.
Applications are made in writing and in good time, and applications on grounds of disability or
chronic illness go to the university's
[representative for students with disabilities or chronic illness](https://www.uni-mannheim.de/en/academics/during-your-studies/studying-with-a-disability-or-chronic-illness/).

::: {.callout-tip}
**Talk to me early, and tell me only what you want to.**
The formal route runs through the representative and the examination board, and I do not need to
know the nature of your condition.
What helps me is knowing early that an adjustment is coming, so it can be built in rather than
improvised.
:::

### Language {#sec-language}

The seminar is taught in English and the readings are in English.
The term paper shall be written in English.

### Mental health support {#sec-mental-health}

Life and study at the University of Mannheim can sometimes feel complicated, challenging, or
overwhelming.
That is completely normal.

If you ever feel mentally or emotionally strained, you may find useful advice on the university's
[good mental health and studying page](https://www.uni-mannheim.de/en/academics/studying-the-healthy-way/good-mental-health/).
The [help in times of crisis page](https://www.uni-mannheim.de/en/academics/studying-the-healthy-way/help-in-times-of-crisis/)
gives an overview of the counselling and support services available at the university.

## AI policy {#sec-ai-policy}

::: {.callout-note}
This stated policy is a first proposal and may be subject to change during the term.
:::

You may use AI assistance, and for some things it is genuinely useful: finding literature,
checking whether an argument holds together, working on your English.

Two conditions.

**Declare it.**
Your term paper carries a short note saying what you used and what you used it for.
A sentence is enough.
An undeclared use is a problem in a way that a declared one is not.

**It does not make the argument.**
The claim, the reasoning and the judgement about what the evidence supports have to be yours,
because they are what is being assessed.
A paper that reads as though nobody decided anything is a weak paper whether or not a model wrote
it, and you are answerable for every sentence you submit, including any citation that turns out
not to exist.

## Session plan {#sec-session-plan}

What each session covers, what you should be able to do afterwards, and what to read.
Dates are on the [Schedule](schedule.qmd).

::: {.callout-note}
This is a preliminary plan and may be revised during the term.
:::

```{r}
#| label: session-plan
#| echo: false
#| message: false
#| warning: false
#| results: asis

# -----------------------------------------------------------------------------
# BUILT from `weeks:` in course.yml, which is also what schedule.qmd reads, so the
# syllabus and the schedule cannot state different topics for the same session.
# Add or reword a session THERE. Dates come from session_dates(), so the numbering
# here matches the schedule exactly.
#
# Readings are emitted as `@key` citations. knitr runs before pandoc, so they are
# processed as ordinary citations and collected under the References heading.
# -----------------------------------------------------------------------------
dates <- session_dates(cfg)

# One bullet: the citation, plus the reading's note when course.yml gives it one.
# The note is plain text after the citation rather than a pandoc locator
# (`@key [chapters 1, 2 and 3]`), because a locator is relabelled by the citation
# style and the page would then stop saying what course.yml says.
bullets_of <- function(entries) {
  cite <- vapply(entries, function(e) {
    if (is.null(e$note)) sprintf("- @%s", e$key) else sprintf("- @%s, %s", e$key, e$note)
  }, character(1))
  paste0(cite, collapse = "\n")
}

emit_readings <- function(cfg, i) {
  core <- reading_entries(cfg, i, "core")
  opt <- reading_entries(cfg, i, "optional")
  if (length(core) == 0 && length(opt) == 0) {
    return(invisible(NULL))
  }
  cat("::: {.session-readings}\n\n")
  if (length(core) > 0) {
    cat("**Core reading**\n\n")
    cat(bullets_of(core), "\n\n", sep = "")
  }
  if (length(opt) > 0) {
    cat("**Optional**\n\n")
    cat(bullets_of(opt), "\n\n", sep = "")
  }
  cat(":::\n\n")
}

for (i in seq_len(cfg$sessions$count)) {
  w <- week_entry(cfg, i)
  if (is.null(w)) {
    next
  }

  cat(
    "### Session ",
    i,
    ": ",
    w$topic,
    " {#sec-session-",
    pad(i),
    "}\n\n",
    sep = ""
  )

  meta <- session_date_label(dates, i, "%d %B %Y")
  blk <- block_name_of(cfg, i)
  if (!is.na(blk)) {
    meta <- paste0(meta, " · ", blk)
  }
  cat("::: {.session-meta}\n", meta, "\n:::\n\n", sep = "")

  if (!is.null(w$content)) {
    cat(trimws(w$content), "\n\n", sep = "")
  }

  goals <- unlist(w$goals)
  if (length(goals) > 0) {
    cat("**Afterwards you will be able to:**\n\n")
    cat(paste0("- ", goals, collapse = "\n"), "\n\n", sep = "")
  }

  emit_readings(cfg, i)
}
```

## References {#sec-references}

::: {#refs}
:::
